Analysis

### 2022-06-06 FIMO_EDA.Rmd
SVG save code

ggplot(pvals, aes(x = `-log10(p-value)`, color = MotifDB)) +
  geom_density() +
  geom_vline(xintercept = -log10(pval_threshold), linetype = "dashed", color = "red") +
  scale_color_manual(values = mycols[1:6]) +
  theme_bw() +
  theme(panel.grid.major = element_blank(), 
      panel.grid.minor = element_blank(), 
      # axis.text.x = element_text(angle = 45, vjust = 1, hjust = 1),
      plot.title = element_text(hjust = 0.5)) +
  ylab("Density")

fileNameOut1 <- file.path(dir_data, "Figure_human_pvalues.svg")
ggsave(filename = fileNameOut1, width = 7, height = 3)
```

@@

ggplot(pvals, aes(x = `-log10(p-value)`, color = MotifDB)) +
  geom_density() +
  geom_vline(xintercept = -log10(pval_threshold), linetype = "dashed", color = "red") +
  scale_color_manual(values = mycols[1:6]) +
  theme_bw() +
  theme(panel.grid.major = element_blank(), 
      panel.grid.minor = element_blank(), 
      # axis.text.x = element_text(angle = 45, vjust = 1, hjust = 1),
      plot.title = element_text(hjust = 0.5)) +
  ylab("Density")

fileNameOut1 <- file.path(dir_data, "Figure_mouse_pvalues.svg")
ggsave(filename = fileNameOut1, width = 7, height = 3)
```

>>>>

ggplot(pvals, aes(x = `-log10(p-value)`, color = MotifDB)) +
  geom_density() +
  geom_vline(xintercept = -log10(pval_threshold), linetype = "dashed", color = "red") +
  scale_color_manual(values = mycols[1:6]) +
  theme_bw() +
  theme(panel.grid.major = element_blank(), 
      panel.grid.minor = element_blank(), 
      # axis.text.x = element_text(angle = 45, vjust = 1, hjust = 1),
      plot.title = element_text(hjust = 0.5),
      legend.text = element_text(size = 6)) +
      # legend.key.height = unit(0.2, "mm"),
      # legend.key.width = unit(5, "mm")) +
  ylab("Density")

fileNameOut1 <- file.path(dir_data, "Figure_human_pvalues.svg")

dev.off()
svg(filename = fileNameOut1, width = 7, height = 3)
print(p)
dev.off()
```

@@

p <- ggplot(pvals, aes(x = `-log10(p-value)`, color = MotifDB)) +
  geom_density() +
  geom_vline(xintercept = -log10(pval_threshold), linetype = "dashed", color = "red") +
  scale_color_manual(values = mycols[1:6]) +
  theme_bw() +
  theme(panel.grid.major = element_blank(), 
      panel.grid.minor = element_blank(), 
      # axis.text.x = element_text(angle = 45, vjust = 1, hjust = 1),
      plot.title = element_text(hjust = 0.5),
      legend.text = element_text(size = 6)) +
      # legend.key.height = unit(0.2, "mm"),
      # legend.key.width = unit(5, "mm")) +
  ylab("Density")

fileNameOut1 <- file.path(dir_data, "Figure_mouse_pvalues.svg")
# ggsave(filename = fileNameOut1, width = 7, height = 3)
dev.off()
svg(filename = fileNameOut1, width = 7, height = 3)
print(p)
dev.off()
```
